\section{Building the Web-Based Interactive Demo}
\label{sec:web}

We built a \emph{static} site in \texttt{web/} so lecture ideas---\emph{pitch vs.\ frequency}, \emph{waveform vs.\ timbre}, and \emph{simple noise}---can be tried in the browser with no backend. The client uses HTML5, CSS, JavaScript, and the \textbf{Web Audio API}; real-time audition and offline export share one synthesis path. Staying static avoided servers, credentials, and databases yet still scales for classroom traffic once GitHub Pages hosts the assets. File boundaries (\texttt{app.js} vs.\ \texttt{audio-engine.js}) also mirrored how we split UI work from DSP during the project.

\subsection{Features and Stack}
Users edit $1$--$16$ steps: duration on a $0.2$--$1.0\,\mathrm{s}$ grid (step $0.1$), pitch on thirteen C-major solf\`{e}ge degrees from low \textit{sol} to high \textit{mi} with Hz labels, waveform (square or sawtooth), and optional noise. A piano-roll score plots time left-to-right; colors distinguish waveforms, hatched blocks mark noise, and clicking a block jumps to that step. During playback an output waveform shows the mix; a master gain slider and \textbf{Export WAV} close the listen--inspect--save loop. The score plus oscilloscope let listeners connect what they hear with one time-aligned trace they can screenshot or archive. A preset loader and \texttt{web/qr-site.png} ease demos and mobile access; the QR target is the public Pages URL below. GitHub Actions publishes \texttt{web/} as the site root from repository \url{https://github.com/Displace1/UCUG1903} (see \texttt{.github/workflows/deploy-pages.yml} and \texttt{README.md}). File roles are listed in Table~\ref{tab:web-files}.

\begin{table}[htbp]
  \centering
  \caption{Web source files and responsibilities}
  \label{tab:web-files}
  \begin{tabular}{@{}ll@{}}
    \toprule
    Path & Role \\
    \midrule
    \texttt{web/index.html} & Structure, controls, canvases \\
    \texttt{web/style.css}   & Layout, theme, readability \\
    \texttt{web/app.js}      & UI state, score/wave drawing, input, engine calls \\
    \texttt{web/audio-engine.js} & Waves, noise, play/stop, WAV render \\
    \texttt{web/song-schema.js}  & Timeline and frequency helpers \\
    \texttt{web/default-song.json} & Default / demo sequence \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Architecture and Core Logic}
Presentation stays in \texttt{app.js} (DOM, canvases, state); \texttt{audio-engine.js} writes samples; \texttt{song-schema.js} fixes timing and frequency fields between them. Figure~\ref{fig:web-arch} shows data flow. Square and sawtooth are generated per step at the audio sample rate. Noise uses a console-style \textbf{15-bit LFSR} and low-pass filtering; tonal and noise buses are scaled (e.g.\ $1/\sqrt{2}$) before summing to limit clipping, as in \texttt{README.md}. Canvas hit-testing maps clicks back to form controls. Offline \texttt{AudioContext} rendering writes the same buffers as audition, wrapped as standard WAV for download, so exported audio matches the synthesized timeline aside from live buffering delay.

\begin{figure}[htbp]
  \centering
  \begin{tikzpicture}[
    box/.style={draw, rounded corners, align=center, minimum width=3.1cm, minimum height=1.05cm},
    font=\small
  ]
    \node[box] (schema) {\textbf{Data conventions}\\\texttt{song-schema.js}};
    \node[box, right=1.2cm of schema] (app) {\textbf{UI / score / waveform}\\\texttt{app.js}};
    \node[box, right=1.5cm of app] (audio) {\textbf{Synthesis \& export}\\\texttt{audio-engine.js}};
    \draw[->, thick] (schema) -- (app);
    \draw[->, thick] (app) -- node[midway, below=0.15cm, font=\scriptsize, inner sep=1pt] {play / render} (audio);
  \end{tikzpicture}
  \caption{Front-end modules and data flow (schematic).}
  \label{fig:web-arch}
\end{figure}

\subsection{Deployment}
Source code and documentation are in \url{https://github.com/Displace1/UCUG1903}. Each push triggers GitHub Actions to deploy \texttt{web/} to GitHub Pages; the public demo is \url{https://displace1.github.io/UCUG1903/}. Prefer \texttt{HTTPS} (or a local HTTP server) over \texttt{file://} for reliable audio. The bundled QR code points to the same site URL for classroom phones.
